Demographic Groups with Stronger Biden Support in the Election Races

### 2024-03-31 paper/paper.qmd
update change

---
title: "Demographic Groups with Stronger Biden Support in the Election Races'"
author: 
  - Yang Zhou
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-State.git >"
date: today
date-format: long
abstract: "This paper explores the relationship between voting preferences and the predictors of education, income, and personal gun ownership in the United States through analyzing 2022 US election database. By examining data from Cooperative Election Study, we identify clear patterns indicating that higher income are more likely to vote for Biden. Besides, the higher personal gun ownership will also significantly increase the likelihood of voting for Biden. By contrast, the people with higher education level show less probability to vote for Biden. Our findings underscore the critical impact of socio-economic status and personal security concerns on electoral outcomes, shedding light on the underlying dynamics that shape voter behavior in contemporary American politics. Ultimately, this research contributes to our understanding of the complex factors that drive electoral decisions, offering valuable insights for policymakers, political strategists, and citizens aiming to foster more informed and equitable democratic processes."

format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Introduction
The goal of the Cooperative Election Study (CES) is to investigate how Americans vote and perceive their electoral experiences, how they hold their representatives accountable in elections, and how their behavior and experiences vary depending on the political climate and social milieu. The Cooperative Election Study (CES) serves as a crucial platform for understanding the complexities of American electoral systems. This paper delves into the findings of the 2022 CES, which aimed to provide insights into voter behavior, perceptions of electoral experiences, and the broader socio-political milieu shaping democratic governance. With a focus on exploring how Americans vote, perceive their electoral experiences, and navigate the political climate, the CES helps us in understanding the electoral outcomes in the United States.

The Cooperative Election Study (CES) addressed gaps in understanding voter behavior by employing a multifaceted approach involving 60,000 cases and 60 research teams. Their methods included pre-election surveys and post-election assessments, providing detailed insights into American elections. Pre-election surveys were filled out on the spot between September 29 and November 8. The Post-election campaigning frenzy took place between November 10 and December 15. For every 1,000 respondents, half of the questions had common material while the other half were fully created and managed by each study team. Questions that are common to all team modules and have a sample size equal to the total sample size of all team modules make up common content. Every one of the sixty teams bought a 1,000-person survey. Every case was chosen online, and YouGov created a corresponding random sample for this investigation. The first data release happened on March 20, 2023. The Harvard University database contains archived and accessible data from this investigation. Vote verification is included in data release 2 for all respondents. The study on CES 2022 is still under progress. Using a large-scale national survey, the Collaborative Congressional Election project was founded in 2006 to investigate congressional elections and representation. The project built upon the analysis conducted by the Public Opinion Research and Training Lab at the Massachusetts Institute of Technology in 2005. Understanding these findings is crucial for policymakers, researchers, and citizens, as they shed light on the complexities of democracy and provide insights to strengthen democratic institutions. This paper aims to dive deeper into the CES findings, analyzing their implications for the future of American democracy.

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}. Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language `R`[@citeR] . The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].

>>>>

---
title: "Demographic Groups with Stronger Biden Support in the Election Races'"
author: 
  - Yang Zhou
thanks: "Code and data are available at: <https://github.com/yangzhoucoco/Political-support-in-the-United-State.git >"
date: today
date-format: long
abstract: "This paper explores the relationship between voting preferences and the predictors of education, income, and personal gun ownership in the United States through analyzing 2022 US election database. By examining data from Cooperative Election Study, we identify clear patterns indicating that higher income are more likely to vote for Biden. Besides, the higher personal gun ownership will also significantly increase the likelihood of voting for Biden. By contrast, the people with higher education level show less probability to vote for Biden. Our findings underscore the critical impact of socio-economic status and personal security concerns on electoral outcomes, shedding light on the underlying dynamics that shape voter behavior in contemporary American politics. Ultimately, this research contributes to our understanding of the complex factors that drive electoral decisions, offering valuable insights for policymakers, political strategists, and citizens aiming to foster more informed and equitable democratic processes."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Introduction
2020 United States Presidential Election stood as an important political event, reflecting societal divisions and highlighting the influence of various demographic factors on voting behavior. This election, which culminated in the victory of Joe Biden over incumbent Donald Trump, has spurred a renewed interest in understanding the dynamics of voter preferences and the underlying factors that drive electoral decisions. Our study aims to dissect the relationship between voters' educational background, income levels, personal gun ownership, and their voting preferences, employing logistic regression analysis to reveal the potential associations between different factors.

The Cooperative Election Study (CES)conduct a throughout survey encompassing a wide range of voter demographics and attitudes.CES collaborate with 60 researches teams to assembles sample comprising 60,000 cases. The cases are based on the survey of adult pariticipants in 2022 fall. YouGov was commissioned to help the teams to conduct national sample surbey. They conducted the survey before and after elections. The first round survey were completed from September 29 to November 8, 2022 and the second period is gathered from November 10 to December 15, 2022. By offering an throughout views to different constituencies, voter demographics and voter behaviors, CES reveals the complexity of electoral behavior and voter demographics. By understanding voter behaviors,, we gain valuable insights that pave the way for refining and advancing democratic practices.

In addition, by leveraging data from the 2022 CES, this paper delves into how variables such as education, income, and gun ownership serve as predictors for electoral choices, specifically the likelihood of voting for Biden or Trump. This analysis not only reveal the individual impact of these factors but also contributes to a broader understanding of the socio-economic and cultural impact of American electoral behavior.

Based on our model, I found that individuals with higher incomes demonstrate a greater propensity to vote for Biden. Additionally, elevated levels of personal gun ownership significantly correlate with an increased likelihood of supporting Biden. Conversely, individuals possessing higher levels of education exhibit a reduced probability of voting for Biden.

To be more specific, this paper is structured as follow: in {#sec-data}, I will introduce the data variable and how the data is used for the overall analysis.Visualization would also be included. In {#sec-model}, I will set up the model to predict the relationship between the predictors and electoral outcomes. Model justification will provide a rationale for selecting logitics model. {#sec-results} is focused on explain the result of the model. Lastly, {#sec-Discussion} provides a discussion on what we found in the model. I will also talk about the weakness of this paper along with the further study on this topic.

I will uses the programming language `R`[@citeR] to analyze the data. `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm] will help me in the model and visualization part.
